Selecting and ranking interesting pairs of cyclic temporal granularities

### 2021-02-10 paper/main.Rmd
size section rough writing

1. Given the data; $\{v_t: t=0, 1, 2, \dots, T-1\}$, the $wpd_norm$ is computed and is represented by $wpd_{obs}$.

@@

3. $wpd_norm$ is computed for the permuted sequence of the data and is represented by $wpd_{perm_1}$.

@@

@@

## Size, power and confidence interval

>>>>

1. Given the data; $\{v_t: t=0, 1, 2, \dots, T-1\}$, the $wpd_{norm}$ is computed and is represented by $wpd_{obs}$.

@@

3. $wpd_{norm}$ is computed for the permuted sequence of the data and is represented by $wpd_{perm_1}$.

@@

The p-value of the design $D_{null}$ is size.
The p-value of other designs is power.
Confidence interval of the

@@

## Size

The p-value is almost always greater than 0.05, which means there is no significant differences between the different categories, which is true from the simulation design.

```{r size}
library(readr)
library(tidyverse)
data_N01 <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds"))

data_N01_obs <- data_N01 %>% filter(perm_id==1)
data_N01_samp <- data_N01 %>% filter(perm_id!=1)

plot_mmpd_null_grid(data_N01_samp, data_N01_obs)

mmpd_dist_null_grid  = data_N01_samp

mmpd_null_orig = data_N01_obs
compute_p_value <- left_join(mmpd_dist_null_grid, mmpd_null_orig,
                               by = c("nx", "nfacet")) %>% 
    group_by(nx, nfacet) %>% 
    summarise(p_value = sum(if_else(abs(value.x)>abs(value.y),1,0))/n(), .groups = 'drop')

  ggplot() + 
    geom_histogram(data = mmpd_dist_null_grid, aes(x = value))  + 
    geom_vline(data = mmpd_null_orig, aes(xintercept = value),colour = "red") +
    geom_text(data = round(compute_p_value, 3), size = 3,  
              aes(x = -Inf,
                  y =  Inf,
                  label = paste("p-value:",p_value),
                  hjust   = 0,
                  vjust   = 1)) + 
    facet_grid(nx ~ nfacet)
```

```{r power}
library(readr)
library(tidyverse)
data_N01 <- read_rds(here("simulations/norm/null_design_quantrans_nperm/data-agg/all_data_wpd_N01.rds"))

data_N01_obs <- data_N01 %>% filter(perm_id==1)
data_N01_samp <- data_N01 %>% filter(perm_id!=1)

plot_mmpd_null_grid(data_N01_samp, data_N01_obs)

mmpd_dist_null_grid  = data_N01_samp

mmpd_null_orig = data_N01_obs
compute_p_value <- left_join(mmpd_dist_null_grid, mmpd_null_orig,
                               by = c("nx", "nfacet")) %>% 
    group_by(nx, nfacet) %>% 
    summarise(p_value = sum(if_else(abs(value.x)>abs(value.y),1,0))/n(), .groups = 'drop')

  ggplot() + 
    geom_histogram(data = mmpd_dist_null_grid, aes(x = value))  + 
    geom_vline(data = mmpd_null_orig, aes(xintercept = value),colour = "red") +
    geom_text(data = round(compute_p_value, 3), size = 3,  
              aes(x = -Inf,
                  y =  Inf,
                  label = paste("p-value:",p_value),
                  hjust   = 0,
                  vjust   = 1)) + 
    facet_grid(nx ~ nfacet)
```
